flowCore: data structures package for flow cytometry data

### 2007-05-30 inst/doc/HowTo-flowCore.Rnw
fix read.FCS function to support NA under the keywords ANASTART ANAEND of the header section
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@24495 bc3139a8-67e5-0310-9ffc-ced21a209358
Add splitScaleTransformation (for transformML) Modify read.FCS to remove random sampling but leave which.lines Add parentId argument in class Filter Fix rectangle gate boundary allow Min>=Max like in GateML standard, return empty gate
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@25068 bc3139a8-67e5-0310-9ffc-ced21a209358

FCS files are read into the R environment via the \Rfunction{read.FCS} function using the standard connection interface---allowing for the possibility of accessing FCS files hosted on a remote resource as well as those that have been compressed or even retrieved as a blob from a database interface.

@@

Finally, when only a particular subset of parameters is desired the \Rfunction{column.pattern} parameter allows for the specification of a regular expression and only parameters that match the regular expression will be included in the frame. For example, to include on the the Height parameters:

<<RedFiles3, echo=true, results=verbatim>>=
x <- read.FCS(file.name,column.pattern="-H")
x
@

@@

@@

These gates are all described in more or less the same manner:

>>>>

FCS files are read into the R environment via the
\Rfunction{read.FCS} function using the standard connection
interface---allowing for the possibility of accessing FCS
files hosted on a remote resource as well as those that have
been compressed or even retrieved as a blob from a database
interface. FCS files (version 2.0 and 3.0) and LMD (List
Mode Data) extensions are currently supported.

@@

When only a particular subset of parameters is
desired the \Rfunction{column.pattern} parameter allows for
the specification of a regular expression and only
parameters that match the regular expression will be
included in the frame. For example, to include on the the
Height parameters:

<<RedFiles3, echo=true, results=verbatim>>= 
x <- read.FCS(file.name, column.pattern="-H") 
x 
@

@@

Finally, only a sample of lines can be read in case you need a quick overview of a large serie of files. 
<<RedFiles3, echo=true, results=verbatim>>= 
lines <- sample(100:500, 50)
y <- read.FCS(file.name, which.lines = lines) 
y 
@

@@

These gates are all described in more or less the same manner (see man pages for more details):
